---
title: "REEM oracle downloads"
author: "Kerim Aydin"
date: "8/24/2022"
output: html_notebook
---
## REEM Diet Composition Tools
This set of tools generates diet composition estimates from REEM BTS data, 
includes queries for bottom-trawl survey data provided by RACE.  This also 
loads user-supplied parameters from user.R (most R files are in the R
subdirectory; user.R is in the top directory).

## Open Oracle connection
```{r query_open, eval=FALSE}
library("RODBC")
library("getPass")
source("R/REEM_download_functions.R")

# add setwd() here if needed - code assumes everything runs from main repo directory
# (subdirectories should include /data and /R").

# oracle.connect input argument is the connection name in installed odbc driver,
# may differ by user (e.g. "AFSC" or "AFSCP1" etc.).  This function should bring
# up a username and password interface to log in to Oracle.
channel <- oracle.connect("AFSC")  
#reem.download.rawfood(channel, path="data/local_reem_data")
reem.download.bts.predprey(channel, path="data/local_reem_data")
reem.download.bts.preylengths(channel, path="data/local_reem_data")

oracle.disconnect(channel)
```

## Querying RACEBASE tables
Here, we download tables from RACEBASE (Oracle tables with names prefixed by RACEBASE
like RACEBACE.HAUL) and save them as .csvs in the given path directory.  This does *not*
put the data in the workspace.  The list of tables can be changed (e.g. to refresh a
single table only).  These queries select all table fields (no data manipulations).
```{r query_RACE, eval=FALSE}
library("RODBC")
library("getPass")
source("R/REEM_download_functions.R")

channel <- oracle.connect("AFSC")  

racebase.tables   <- c("CATCH", "HAUL", "LENGTH", "SPECIMEN", "STRATUM", "STATIONS",
                       "SPECIES", "CRUISE", "SPECIES_CLASSIFICATION") #"SIZECOMP_TOTAL"

racebase.download(channel, tables=racebase.tables, path="data/local_racebase")

oracle.disconnect(channel)

```
