---
title: "REEM oracle downloads"
author: "Kerim Aydin"
date: "8/24/2022"
output: html_notebook
---
## REEM Diet Composition Tools
This set of tools generates diet composition estimates from REEM BTS data, 
includes queries for bottom-trawl survey data provided by RACE.  This also 
loads user-supplied parameters from user.R (most R files are in the R
subdirectory; user.R is in the top directory).

## Open Oracle connection
```{r query_open, eval=FALSE}
library("RODBC")
library("getPass")
source("R/REEM_download_functions.R")

# add setwd() here if needed - code assumes everything runs from main repo directory
# (subdirectories should include /data and /R").

# oracle.connect input argument is the connection name in installed odbc driver,
# may differ by user (e.g. "AFSC" or "AFSCP1" etc.).  This function should bring
# up a username and password interface to log in to Oracle.
channel <- oracle.connect("AFSC")  

```

## Querying RACEBASE tables
Here, we download tables from RACEBASE (Oracle tables with names prefixed by RACEBASE
like RACEBACE.HAUL) and save them as .csvs in the given path directory.  This does *not*
put the data in the workspace.  The list of tables can be changed (e.g. to refresh a
single table only).  These queries select all table fields (no data manipulations).
```{r query_RACE, eval=FALSE}

racebase.tables   <- c("CATCH", "HAUL", "LENGTH", "SPECIMEN", "STRATUM", "STATIONS",
                       "SPECIES", "CRUISE", "SPECIES_CLASSIFICATION", "SIZECOMP_TOTAL")

racebase.download(channel, tables=racebase.tables, path="data/local_racebase")

```

## Querying REEM diet tables
This loads REEM data.  These are not loaded completely "RAW", the query script
performs some lookups on the Oracle end as contained in these scripts, and
does not pull all fields.  It selects
```{r query_REEM, eval=FALSE}

# TODO - find query to join EBS strata to GOA/AI strata
#query.to.csv(channel, query="SELECT * FROM GOA.GOA_STRATA", file="data/goa_strata.csv")
query.to.csv(channel,  query="SELECT * FROM FOODLAB.NODC", file="data/local_reem_data/nodc.csv")

# Predprey queries
reem.download.bts.predprey(channel, region="EBS", path="data/local_reem_data") 
reem.download.bts.predprey(channel, region="GOA", path="data/local_reem_data") 
reem.download.bts.predprey(channel, region="AI",  path="data/local_reem_data") 

# Prey length query
reem.download.bts.preylenths(channel, region="EBS", path="data/local_reem_data")
reem.download.bts.preylenths(channel, region="GOA", path="data/local_reem_data")
reem.download.bts.preylenths(channel, region="AI",  path="data/local_reem_data")

```

## Closing the connection once finished
```{r query_close, eval=FALSE}

oracle.disconnect(channel)

```


